Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-01 docs/00-manuscripts/ieee/ieee-manuscript.tex
rephrase disc: feature set differences

\subsubsection{Feature set differences}
One objective which this study aimed to answer was whether expert-based or data-driven feature engineering has a positive influence on model performance.
With respect to \autoref{fig:perf-result} one can say that overall the different feature sets did not result in substantial and consistent changes in performance.
RF and XGBoost showed a somewhat surprising decrease in performance of about six percentage points on task VI compared to all others.
We have no explanation for this specific result, especially because the best performing SVM model does not reflect this difference.
In addition, all learners showed a slightly better average performance on feature sets which included NRIs (e.g. NRI-VI, HR-NRI, HR-NRI-VI) than on those which did not (i.e. VI and HR only).

>>>>

\subsubsection{Feature set differences}
One objective which this study aimed to answer was whether expert-based or data-driven feature engineering has a positive influence on model performance.
With respect to \autoref{fig:perf-result}, no overall trend was found for all models that related to specific feature sets.
The performance of RF and XGBoost on the VI feature set was about six percentage points lower than on others.
One reason could be the lack of coverage in the wavelength area between 810 nm and 1000 nm (\autoref{fig:fi-permut-vi-hr}).
In addition, for all learners but SVM a better performance was observed when NRI indices were included in the feature set (i.e. NRI-VI, HR-NRI, HR-NRI-VI).
